---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# val.report <a href="https://pharmar.github.io/val.report/"><img src="man/figures/logo.svg" align="right" height="139" alt="val.report website" /></a>

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/pharmaR/val.report/graph/badge.svg)](https://app.codecov.io/gh/pharmaR/val.report)
[![R-CMD-check](https://github.com/pharmaR/val.report/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/pharmaR/val.report/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of val.report is to documents results of package checks for validation.

## Installation

You can install the development version of val.report from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("pharmaR/val.report")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r cleanup, echo=FALSE}
unlink("pkgdown/assets/*")
```

```{r example}
library(val.report)
# Specify the folder where the files should go (here for easy access on the website)
options("valreport_output_dir" = "pkgdown/assets")
pr <- package_report(
  package_name = "dplyr",
  package_version = "1.1.4",
  params = list(
    assessment_path = system.file("assessments/dplyr.rds", package = "val.report")),
  quiet = TRUE # To silence quarto output for readability
)
pr
```

We first selected were reports should go.
Then we used [{riskmetric}](https://cran.r-project.org/package=riskmetric) data to generate the report for the package.

Then we can access those files on the website:

 - [HTML](https://pharmar.github.io/val.report/validation_report_dplyr_v1.1.4.html)
 - [markdown](https://pharmar.github.io/val.report/validation_report_dplyr_v1.1.4.md)
