---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# val.report <a href="https://pharmar.github.io/val.report/"><img src="man/figures/logo.svg" align="right" height="139" alt="val.report website" /></a>

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/pharmaR/val.report/graph/badge.svg)](https://app.codecov.io/gh/pharmaR/val.report)
[![R-CMD-check](https://github.com/pharmaR/val.report/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/pharmaR/val.report/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

_documents package validation checks_

## Installation

You can install the development version of val.report from
[GitHub](https://github.com/pharmaR/val.report) with:

``` r
# install.packages("pak")
pak::pak("pharmaR/val.report")
```

## Quick Start

Generate reports easily

```{r example, eval=FALSE}
library(val.report)

options(
  width = 80L,
  val.meter.logs = TRUE,
  val.meter.policy = val.meter::policy(permissions = TRUE)
)

package_report("praise")
```

Because we've given `val.meter` permission to download packages from the
network, passing simply a package name will pull the latest version from
a package repository for evaluation.

If you'd like to be more prescriptive, you can also pass a local source code
directory or package archive (`.tar.gz` or `.zip`). `package_report` accepts
any input that can be converted into a `val.meter::pkg` object.

> [!NOTE]
>
> We are continuing to add more supported input types. Currently, locally source
> code directories have the best support to cover the most concrete use case.
> We plan to improve support for more user-friendly inputs such as packages by
> name and `.tar.gz` by url.

## For Developers

This repository vendors the R Validation Hub quarto template, which is
included as a `git` submodule. Submodules require slightly different syntax
in order to be included. When cloning, be sure to use:

```sh
git clone --recurse-submodules ...  
```
